Verifying Demonstrations

### 2018-11-16 paper/protest-model.tex
Fixes formulas, math mode for strength function

The strength function \(\str\) can be used to regulate the trust in the participation count estimated. In general, \(\str\) can be defined as a weighted sum of the proof shares, $\str = \sum \omega_i.s_i$, with the weights $\omega_i$ being the trust in the witness corresponding to that proof share $s_i$, and the threshold $\theta$ represents the total trust needed to accept a participant as valid.
One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the weights would be 1 for trusted witnesses and 0 for any other witness, and
setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
Finally, both approaches can be combined by giving a weight of 1 to all non-trusted witnesses and a weight of $\theta$ to trusted witnesses. This results in a participant being valid if they are witnessed either by $\theta$ non-trusted witness or by one trusted witness.

\simon{check the notation in the weights formula is consistent, check that the description in section V corresponds}

>>>>

The strength function \(\str\) can be used to regulate the trust in the 
participation count estimated. In general, \(\str\) can be defined as a 
weighted sum of the proof shares, \(\str = \sum \omega_i s_i\), with the 
weights \(\omega_i\) being the trust in the witness corresponding to that proof 
share \(s_i\), and the threshold \(\theta\) represents the total trust needed 
to accept a participant as valid.
One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the weights would be 1 for trusted witnesses and 0 for any other witness, and
setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
Finally, both approaches can be combined by giving a weight of 1 to all 
non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
results in a participant being valid if they are witnessed either by \(\theta\) 
non-trusted witness or by one trusted witness.

\simon{check the notation in the weights formula is consistent, check that the description in section V corresponds}
\daniel{Fixed formula, math mode; didn't check Section V though.}
